---
title: "Shiny Application Reproducible Pitch Presentation"
author: "Sophie Yang"
date: "4/19/2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Overview

This Shiny Application was built as part of the **Developing Data Product** Course Project. 

The GitHub repository containing related codes is located at https://github.com/SY428/ShinyApp.

The Shiny Application can be accessed at: https://sy428.shinyapps.io/ShinyApp.

## European Stock Market Data 

This Shiny Application is designed to help the user interactively view the 4 indexes of the European Stock Market and how they changed over time. An interactive plot for the dataset **EuStockMarkets** allows the user to select up to 4 different stocks between the time frame of 1991 to 1999:

1. DAX - Deutscher Aktienindex, German Stock Index
2. SMI - Swiss Market Index
3. CAC - Cotation Assistée en Continu 40 Index
4. FTSE - Financial Times Stock Exchange 100 Index

A slider bar accesses the time frame (in years) for the user to access the range of stock price data of any of the 4 stocks between any number of years from 1991 to 1999.

## EuStockMarkets Dataset

```{r results='hide', message=FALSE, warning=FALSE, echo=FALSE}
library(shiny)
library(plotly)
library(tidyr)
library(dplyr)
```
```{r}
data("EuStockMarkets");
head(EuStockMarkets,5)
```

Data reorganized vs Time

```{r}
stocks <- as.data.frame(EuStockMarkets) %>%
          gather(index, price) %>%
          mutate(time = rep(time(EuStockMarkets),4))
head(stocks)
```

## Interactive Plot of All 4 Indexes

```{r message=FALSE, warning=FALSE}
plot_ly(stocks, x = stocks$time, y = stocks$price, color = stocks$index) %>%
        layout(title = "European Stock Market Prices", 
               yaxis = list(title = "Stock Price"), 
               xaxis = list(title = "Year"))
```